Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-04 apples_and_oranges.qmd
several simplifications for now, will work more on it later. Also added a sensitivity analysis at the end.

df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))

@@

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type, treatment = descr_active,
                                baseline_n = baseline_n_active)

@@

# specify the model 
model_1 <- as.formula(~ four_level_var)

# run the metaregression
list_model_1_meta_reg <- list()

  list_model_1_meta_reg[[i]] <- rma(yi = cohens_d, 
                                    sei = simulated_se, 
                                    data = list_df_simulated[[i]] , 
                                    method = "ML", 
                                    mods = model_1 , 
                                    test = "knha")

@@

>>>>

@@

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type,treatment = descr_active,
                                baseline_n = baseline_n_active)

@@

# create a function for metaregression

run_metaregression <- function(list_of_datasets, model_formula) {
  list_model_meta_reg <- list()

  for (i in seq_along(list_of_datasets)) {
    list_model_meta_reg[[i]] <- metafor::rma(yi = cohens_d,
                                             sei = simulated_se,
                                             data = list_of_datasets[[i]],
                                             method = "ML",
                                             mods = model_formula,
                                             test = "knha")
  }

  return(list_model_meta_reg)
}

model_1 <- as.formula(~ four_level_var)
list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)

@@

We then examined whether restricting studies to the trials (US-) licensed medication fluoxetine and escitalopram and the most widely used and evidence-based psychological treatment, namely CBT would change results. As can be seen, the coefficient of the difference between placebo and psychotherapy control condition is very strong as judged by the z-value of the difference (8.8), and comaprable to the overall results.

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# filter dataset to include only those ids with cbt fluox or escitalopram

# grab those ids
cbt_fluox_esc_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

# subset all dataframes in the list
list_cbt_fluox_esc_study <- list()

list_cbt_fluox_esc_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
                                                        %in% cbt_fluox_esc_study_ids,]

# use this model as above
model_1 <- as.formula(~ four_level_var)

# apply the function to the list of cbt, fluox, esc
list_model_1_meta_reg_cbt_fluox_esc <- run_metaregression(list_cbt_fluox_esc_study, model_1)

# now use the function to extract the coefficients

list_model_1_meta_reg_cbt_fluox_esc[[1]]
```
